The Astropy Project

### 2017-12-11 main.tex
next section edits

For resolving disagreements about the \astropypkg core package or other \astropy-managed code, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as a ``tie-breaker.''
The committee also oversees affiliated package applications to ensure they are
in keeping with \astropy's vision and
philosophy,\footnote{\url{http://docs.astropy.org/en/stable/development/vision.html}}
as well as the associated procedures.
Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (the body that holds any potential funding in trust for \astropy) or the American Astronomical Society (AAS).

>>>>

For resolving disagreements about the \astropypkg core package or other \astropy-managed code, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as a ``tie-breaker.''
The committee also oversees affiliated package applications to ensure that they
are in keeping with \astropy's vision and
philosophy,\footnote{\url{http://docs.astropy.org/en/stable/development/vision.html}}
as well as the associated procedures.
Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (the body that holds any potential funding in trust for \astropy) and the American Astronomical Society (AAS).
